Multi-state modelling with R: the {\tt msm} package \vskip 0.2in \large{Version <<echo=FALSE,results=tex>>= cat(version) @ \vskip 0.1in <<echo=FALSE,results=tex>>= cat(format(Sys.time(), " @ }

### 2009-11-13 src/doc/msm-manual.Rnw
version 0.9.4

\item[Convergence criteria] ``False convergence'' can sometimes be
  solved by tightening the criteria (\Rfunarg{reltol}, defaults to
  \texttt{1e-08}) for reporting convergence of the optimisation. For
  example, \Rfunarg{control = list(reltol = 1e-16)}.

>>>>

\item[Convergence criteria] ``False convergence'', in which
  \Rfunction{optim()} reports convergence of the optimisation but the
  Hessian is not positive definite, can sometimes be solved by
  tightening the criteria (\Rfunarg{reltol}, defaults to
  \texttt{1e-08}) for reporting convergence. For example,
  \Rfunarg{control = list(reltol = 1e-16)}.
